Review of Group 8 by Group 1

### 2015-02-24 rmtw/a3_review/latex8.tex
lol
Added in the part which didn't make sense

\documentclass[times, 10pt,twocolumn]{IEEEtran} 
\usepackage{latex8}
\usepackage{times}

@@

% author names and affiliations
\author{\IEEEauthorblockN{
  John Burchell\IEEEauthorrefmark{1} and
  William Granli\IEEEauthorrefmark{1}}

  \IEEEauthorblockA{\IEEEauthorrefmark{1}john.a.burchell, william.granli@gmail.com}

}

@@

``The introduction was once again very well written. Good use of italicising the new and key terms. '' However reads very strangely, I presume this was an oversight? The first paragraph of the related work section also sounds a little strange. The related work does a great job of giving a good background and introduction into. It seems to have been very well researched and there are convincing arguments for inclusions and exclusions of concepts.

>>>>

\documentclass[times, 10pt,twocolumn]{article} 
\usepackage{latex8}
\usepackage{times}

@@

% author names and affiliations
\author{John Burchell and William Granli \\
john.a.burchell@gmail.com, william.granli@gmail.com}

@@

``consider the personal fulfilment factors related to qualities such as personal fulfilment factors related to qualities such as engagement,'' Reads very strangely, I presume this was an oversight? The first paragraph of the related work section also sounds a little strange. The related work does a great job of giving a good background and introduction into. It seems to have been very well researched and there are convincing arguments for inclusions and exclusions of concepts.
